### 2020-02-29 README.Rmd
Fix #18

@@

The `retreive()` verb (subject to change), provides a wrapper around `query` that always returns exactly one local path to requested content.  It will check for a stored copy of the content first, and download (and verify) remote content otherwise:

>>>>

The design and implementation of `contenturi` draws from [Preston](https://github.com/bio-guoda/preston), a biodiversity dataset tracker, and [Elton](https://github.com/globalbioticinteractions/elton), a command-line tool to update/clone, review and index existing species interaction datasets.

@@

The `retrieve()` verb (subject to change), provides a wrapper around `query` that always returns exactly one local path to requested content.  It will check for a stored copy of the content first, and download (and verify) remote content otherwise:
